---
title: "Gentle Introduction to *R* by DraCor Walkthrough"
format: html
---

::: {.panel-tabset}

## DraCor

<iframe src="https://dracor.org/" width="100%" height="500px">
</iframe>

## DraCor R library

<iframe src="https://github.com/dracor-org/rdracor" width="100%" height="500px">
</iframe>

:::

---
## Setup {.tabset}

### Command

```{r}
library(rdracor)
library(tidyverse)
```

### Explanation

We loaded libraries that provide specific functions that can be used in our project. The base `R` language is made of general purpose functions and objects. Libraries build upon these to provide

#### Advantages of using libraries

- they simplify things
- they are likely to be well-tested (unlike your code)

:::

## First call to DraCor API


```{r}
corpora <- get_dracor_meta()
class(corpora)
colnames(corpora)
```



```{r}
shake_corpus <- get_dracor(corpus = "shake")
head(shake_corpus) %>% 
  knitr::kable(format = "html")
```

```{r}

tempest_text <- rdracor::get_play_spoken_text(corpus = "shake", play = shake_corpus$playName[1])
#head(tempest)
```
